\documentclass[a5paper, twoside]{report}

\usepackage{array}
\usepackage{arydshln}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage[margin=2cm]{geometry}
\usepackage[hidelinks, pdfusetitle]{hyperref}
\usepackage{lastpage}
\usepackage{mdframed}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{nameref}
\usepackage{parskip}
\usepackage{tgtermes}
\usepackage[center]{titlesec}
\usepackage{varwidth}

\author{Achernar}
\title{The Bedrock Manual}
\date{2025-04-12}

\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\pagestyle{fancy}
\fancypagestyle{plain}{\pagestyle{fancy}}
\fancyhf{}
\fancyhead[lo,re]{\small\bfseries\thechapter.\ \MakeUppercase{\leftmark}}
\fancyfoot[lo,re]{\small\bfseries \thepage\ / \pageref*{LastPage}}

\titleformat{\chapter}{\flushright\huge\bfseries}{}{0pt}{\thechapter.\ }[]
\titleformat{\section}{\large\bfseries}{}{0pt}{\thesection.\ }[]
\titleformat{\subsection}{\centering\small\bfseries}{}{0pt}{\thesubsection.\ }[]

\titlespacing*{\chapter}{0pt}{0pt}{0pt}
\titlespacing*{\section}{0pt}{0.5cm}{0.5cm}
\titlespacing*{\subsection}{0pt}{0.25cm}{0.25cm}

\setlength{\columnsep}{1cm}

\newcommand*{\rulewidth}{0pt}
\renewcommand*{\headrulewidth}{\rulewidth}
\renewcommand*{\footrulewidth}{\rulewidth}

\begin{document}
	\thispagestyle{empty}
	\pagenumbering{gobble}cent

	\begin{center}
		{\small\ttfamily bedrock 0.5.0-7}

		\vspace*{\fill}
		{\large\bfseries The}

		{\huge\bfseries Bedrock Manual}

		{\large\bfseries 0.5}

		\vspace*{\fill}
		{\small Copyright \textcopyright\ 2025 Gabriel Bjørnager Jensen}
	\end{center}

	\clearpage
	\pagenumbering{arabic}
	\tableofcontents
		\label{content}
	\addcontentsline{toc}{chapter}{\numberline{\thechapter}\contentsname}

	\clearpage
	\chapter{Introduction}
		\label{intro}
		\textit{Bedrock} is an artillery video game developed at Achernar.

		This manual describes the basics of the game, including how to set it up, how gameplay works, and more.

		\section{Technical requirements}
			\begin{mdframed}
				\small\itshape\bfseries
				Note: Bedrock is still early in its development, and not all platforms may yet have been thoroughly tested.
			\end{mdframed}

			\subsection{Machine architecture}
				Bedrock requires at least \texttt{32} bits per memory address.
				So far, Bedrock has been tested to work on AMD64 (x86-64) machines, and support is therefore also expected on IA-32 (specifically i686-compatible variants).
				Other architectures have not been tested yet.

			\subsection{Operating system}
				Bedrock is written to support UNIX-compatible systems as well as Microsoft Windows.
				So far, however, only Linux has been tested (specifically Arch Linux).

			\subsection{Graphics interface}
				Bedrock can make use of any of the following windowing protocols, depending on the target operating system:

				\begin{multicols}{2}
					\begin{itemize}
						\item{Cocoa}
						\item{Orbital}
						\item{X}
						\item{Wayland}
						\item{Win32}
					\end{itemize}
				\end{multicols}

				Additionally, rendering is done using any of the following interfaces:

				\begin{multicols}{2}
					\begin{itemize}
						\item{Direct3D}
						\item{Metal}
						\item{OpenGL}
						\item{Vulkan}
					\end{itemize}
				\end{multicols}

		\section{Contact}
			For support regarding Bedrock, please write an e-mail to Achernar at:

			\begin{mdframed}
				\ttfamily
				gabriel@achernar.io
			\end{mdframed}

	\clearpage
	\chapter{Installation}
		\label{install}
		This chapter will go over the different ways of installing Bedrock.

		{\small\itshape\bfseries Note: For manually installing Bedrock from sourcs, please refer to the ``\nameref{dev}'' chapter.}

		\section{Arch Linux}
			\label{install:arch}
			Use the official PKGBUILD file at:

			\begin{mdframed}
				\url{https://mandelbrot.dk/pkgbuild/bedrock.git}
			\end{mdframed}

		\section{Other systems}
			\label{install:other}
			Please refer to the \textit{\nameref{dev}} chapter.

	\clearpage
	\chapter{Gameplay}
		\label{gameplay}
		Bedrock is of the ``artillery'' genre, a subgenre of strategy games.

		In short: The objective of the ``game'' is to explode your friends.

		\section{Controls}
			\label{gameplay:controls}
			Characters are controled using the keyboard.
			Joypad support is planned for the future.
			Controls are identical for each player.

			\begin{figure}[h!]
				\begin{tabular}{lcl:l}
					\multicolumn{3}{>{\bfseries}c}{Input} & \multicolumn{1}{>{\bfseries}c}{Action} \\
					\hline
					ESC   &   &                      & Pause game \\
					Q     &   &                      & Quit game \\
					      &   &                      & \\
					CTRL  & + & MWheel $\uparrow$    & Zoom in \\
					CTRL  & + & MWheel $\downarrow$  & Zoom out \\
					Shift & + & MWheel $\uparrow$    & \multirow{2}*{Pan up} \\
					      &   & MWheel $\leftarrow$  & \\
					Shift & + & MWheel $\downarrow$  & \multirow{2}*{Pan down} \\
					      &   & MWheel $\rightarrow$ & \\
					      &   &                      & \\
					+     &   &                      & Increase TPS \\
					-     &   &                      & Derease TPS \\
					\hline
				\end{tabular}
			\end{figure}

	\clearpage
	\chapter{Development}
		\label{dev}
		This section will guide you on how to retrieve the sources for Bedrock, and how to use these sources.
		Instructions must sometimes be done in a terminal emulator.

		\section{Prerequisites}
			\label{dev:prerequisites}
			The following, other programmes must be installed on the host system when building Bedrock from sources:

			\begin{multicols}{2}
				\begin{itemize}
					\item{Git}
					\item{The rustc compiler}
					\item{The Cargo build system}
				\end{itemize}
			\end{multicols}

			See \url{https://git-scm.com/downloads/} on how to install Git.
			See \url{https://www.rust-lang.org/} for information on how to install the Rust programming language.

		\section{Getting the sources}
			\label{dev:source}
			The repositories containing the sources for Bedrock may be any of:

			\begin{mdframed}
				\url{https://mandelbrot.dk/achernar/bedrock.git}

				\url{https://gitlab.com/primuseridani/bedrock.git}

				\url{https://github.com/primuseridani/bedrock.git}
			\end{mdframed}

			Instruct Git to download the desired repository:

			\begin{mdframed}
				\ttfamily
				git clone -{}-depth 0 \textit{repository}
			\end{mdframed}

			... wherein \textit{repository} is the address of the Bedrock repository.
			Git will then unpack the repository into a \texttt{bedrock} directory relative to the current working directory.

		\section{Building}
			\label{dev:building}
			Once downloaded, the sources must be compiled into the final executable.

			Change the working directory into the newly-created \texttt{bedrock} directory:

			\begin{mdframed}
				\ttfamily
				cd bedrock
			\end{mdframed}

			And then invoke Cargo via:

			\begin{mdframed}
				\ttfamily
				cargo build -{}-release
			\end{mdframed}

			When compilation has finished -- which can take quite some time -- the final binary should be located inside a new \texttt{target} directory.

		\section{Installation, UNIX\textsuperscript{\textregistered}}
			\label{dev:unix-install}
			Finally, the installation script \texttt{install.sh} can be used to install the executable, along with some other files:

			\begin{mdframed}
				\ttfamily
				./install.sh \textit{base\_directory}
			\end{mdframed}

			... wherein \texttt{\itshape base\_directory} denotes a custom root directory.
			The script will then populate the following subdirectories of the specified root directory:

			\begin{itemize}
				\ttfamily

				\item{usr/bin}
				\item{usr/share/applications}
				\item{usr/share/pixmaps}
			\end{itemize}

			\begin{mdframed}
				\small\itshape\bfseries
				Hint: Remember to take note of the script's output, as this may be needed when uninstalling Bedrock.
			\end{mdframed}

		\section{Installation, Windows\textsuperscript{\textregistered}}
			\label{dev:windows-install}
			Currently, Bedrock does not provide an out-of-the-box, automated means of installation on Microsoft Windows systems.

	\clearpage
	\chapter{Acknowledgements}
		\label{acknowledge}
		\section{Bedrock}
			Bedrock is copyright \copyright\ 2025 Gabriel Bjørnager Jensen.
			All rights reserved.

		\section{The Bedrock Manual}
			This manual is copyright \textcopyright\ 2025 Gabriel Bjørnager Jensen.
			It is licensed under a Creative Commons Attribution-ShareAlike 4.0 International licence.
			See \url{https://creativecommons.org/licenses/by-sa/4.0/} for more information.

		\section{Trade marks}
			Cocoa, \nobreak{MacOS}, and Metal are registered trade marks of Apple Inc. in the E.U.;
			Linux is a registered trade mark of Linus Benedict Torvalds in the E.U.;
			OpenGL is a registered trade mark of Hewlett Packard Enterprise Development LP in the E.U.;
			UNIX and X are registered trade marks of the Open Group Limited in the E.U.;
			Vulkan is a registered trade mark of the Khronos Group Inc. in the E.U.;
			Windows is a registered trade mark of Microsoft Corporation in the E.U.
\end{document}
